Shallow EDSLs and Object-Oriented Programming

### 2018-12-17 Programming19/Main.tex
Acknowledgment
Code
Minor changes

\paperdetails{
  %% perspective options are: art, sciencetheoretical, scienceempirical, engineering.
  %% Choose exactly the one that best describes this work. (see 2.1)
  perspective=art,
  %% State one or more areas, separated by a comma. (see 2.2)
  %% Please see list of areas in http://programming-journal.org/cfp/
  %% The list is open-ended, so use other areas if yours is/are not listed.
  area={Domain-Specific Languages, Modularity and separation of concerns},
  %% You may choose the license for your paper (see 3.)
  %% License options include: cc-by (default), cc-by-nc
  % license=cc-by,
}

@@

{\bf Importance.} This work is important for two reasons.
Firstly, from an intellectual point of view, this work
establishes the connection between shallow embeddings and OOP, which enables a
better understanding of both concepts. Secondly, this work
offers new programming techniques that can be used to improve 
the modularity and reuse of shallow EDSLs.  
\end{abstract}

>>>>

\paperdetails{
  %% perspective options are: art, sciencetheoretical, scienceempirical, engineering.
  %% Choose exactly the one that best describes this work. (see 2.1)
  perspective=art,
  %% State one or more areas, separated by a comma. (see 2.2)
  %% Please see list of areas in http://programming-journal.org/cfp/
  %% The list is open-ended, so use other areas if yours is/are not listed.
  area={Domain-Specific Languages, Modularity and Separation of Concerns},
  %% You may choose the license for your paper (see 3.)
  %% License options include: cc-by (default), cc-by-nc
  % license=cc-by,
}

@@

{\bf Importance.} This work is important for two reasons.
Firstly, from an intellectual point of view, this work
establishes the connection between shallow embeddings and OOP, which enables a
better understanding of both concepts. Secondly, this work
illustrates programming techniques that can be used to improve 
the modularity and reuse of shallow EDSLs.  
\end{abstract}
